### 2011-12-11 plos_template.tex
some more writing-stuff

% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\section*{Materials and Methods}
\subsection*{Survey on Sharing Genetic Information}
Done in Google Docs, questions on age, chromosomal sex, ethnicity, if they are already customer of a DTC company/planning to become one/don't plan to become one. If they are already a customer: Are they already sharing and are they already sharing phenotypic information? How strong on a scale of 1 = strongly disagree to  5 = strongly agree how do they feel about reasons to share their genetic data because... a) they want to help scientists b) get a personal benefit out of it (new treatments for illnesses) c) because of curiosity d) because it might bring relevant, personalized advertising. How strong on a scale of 1 = strongly disagree to 5 = strongly agree would they feel about not sharing their data because... a) they fear discrimination b) it is a breach of their privacy c) because of negative side-effects for their next of kin d) because they fear personalized spam.

The results were analyzed in somestatisticstool.

>>>>

% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\section*{Materials and Methods}
\subsection*{Survey on Sharing Genetic Information}
The survey was done with Google Docs and included questions on the age, chromosomal sex and ethnicity of the participants. Additionally it included questions on if they are already customer of a DTC company, are planning to become one or don't plan to become one. If they are already a customer they also got asked if they already share their genetic and phenotypic data. All participants got asked if they would share their genetical or phenotypic information with their DTC company, possible answers were "Yes", "Yes, but only if they did not share my medical information with anybody else" and No".

The survey also asked some scale-questions which measured how strong participants agree/disagree on different reasons to share or not to share their information with third parties. The scale went from 1 = strongly disagree over 3 = neutral to  5 = strongly agree. Motivations given to share data were "because you want to help scientists with their research", "because of possible personal benefits (e.g. getting treatments for a disease you have, possibility of new medication, etc.)", "because it may deliver advertising that is relevant to me" and "out of curiosity". Motivations given not to share data were "because advertisers could use the information for targeted campaigns", "because of possible negative consequences for closely related persons", "because of the breach of your privacy" and " because of the fear of discrimination (e.g. by the employer, the state, some insurance company)". Additionally participants had the possibility to give own reasons to share or not to share their data.

The results were analyzed with SPSS 19.
